---
title: "Assignment 1"
author: "Sungjoo Cho"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
```

## create a new project and set-up the project structure (folder, README, etc.)


## download two dataset about COVID-19 from this GitHub repository: “UID_ISO_FIPS_LookUp_Table” and “time_series_covid19_confirmed_global”. Save both data locally

```{r}
count_city_github_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/UID_ISO_FIPS_LookUp_Table.csv?raw=true"
count_city <- read.csv(count_city_github_url)

timeseries_github_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv?raw=true"
timeseries <- read.csv(timeseries_github_url)

# save locally
save(count_city, file = "original_count_city.csv")
save(timeseries, file = "original_timeseries.csv")
```

## merge the two datasets and create a long version of the data. Save both long and wide data locally

```{r}
# creating Combined_Key variable in timeseries
timeseries$Combined_Key <- ifelse(is.na(timeseries$Province.State) | timeseries$Province.State == "",
                                   timeseries$Country.Region,
                                   paste(timeseries$Province.State, timeseries$Country.Region, sep = ", "))

# merging data (wider format)
covid <- timeseries %>%
  left_join(count_city, by = "Combined_Key") %>%
  select(-c(Province.State, Country.Region, Lat.x, Long))

# longer  
covid_longer <- covid %>%
  pivot_longer(
    cols = !c(Combined_Key, UID, iso2, iso3, code3, FIPS, Admin2, Province_State, Country_Region, Lat.y, Long_, Population),
    names_to = "time",
    values_to = "case"
  )

# remove X
covid_longer$time <- gsub("^X", "", covid_longer$time)

save(covid, file = "covid_wide.csv")
save(covid_longer, file = "covid_long.csv")
```

## create three graphs using ggplot and save them

### i) overall change in time of log number of cases

### ii) change in time of log number of cases by country

### iii) change in time by country of rate of infection per 100,000 cases

## use the README file to write a mini-report (10%). It should include:



