---
title: "Assignment 1"
author: "Sungjoo Cho"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(tidyverse)
```

## create a new project and set-up the project structure (folder, README, etc.)


## download two dataset about COVID-19 from this GitHub repository: “UID_ISO_FIPS_LookUp_Table” and “time_series_covid19_confirmed_global”. Save both data locally

```{r}
UID_github_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/UID_ISO_FIPS_LookUp_Table.csv"
UID <- read.csv(UID_github_url)

timeseries_github_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"
timeseries <- read.csv(timeseries_github_url)
```

## merge the two datasets and create a long version of the data. Save both long and wide data locally

```{r}

```

## create three graphs using ggplot and save them

### i) overall change in time of log number of cases

### ii) change in time of log number of cases by country

### iii) change in time by country of rate of infection per 100,000 cases

## use the README file to write a mini-report (10%). It should include:



